\textbf{Emergency Service Location Optimization in a Multi-Zone District based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex
Adding bibliography

\tableofcontents
\newpage
\section{Problem Restatement}
Given a district made up of six separate zones and average travel times between zones, create a model to optimize the placement of $n$ ambulances in order to maximize the number of civilians reached in an eight minute period. Consider the scenarios where $n = 3$, $n = 2$, and $n = 1$, respectively, and for each scenario, keep track of how many people are not being reached with each possible solution.

Then, consider a scenario in which a large scale disaster affects a single location (e.g. the September 11th attacks), and discuss how an Emergency Service Coordinator would cover the situation. Examine how a real-world city or district would prepare for such a disaster. Finally, write a two page memo detailing the model and its analysis for the Emergency Service Coordinator.

\section{Assumptions and Justifications}
\begin{description}
    \item[TODO(drew): Add these assumptions] \hfill \\
    	* Each zone is not a point, but rather a distribution. We experimented with...
	* Route frequency is correlated with population frequency (two random variables?)
    \item[1. Naming] \hfill \\
    	A district is another name for a county. ... TODO(drew)
	Travel...
    \item[2. Zone to Zone Travel] \hfill \\
    	The travel times given are considered to be optimal routes from the center of one zone to the center of the another, regardless of any other zones that may lie in between.
    \item[3. Travel Inside Each Zone] \hfill \\
    	The travel times given for travel from any zone to itself is the average
        of all the travel times of the different routes within that zone.
    \item[4. Directional Travel Inside Each Zone] \hfill \\
    	The ratio between the time it takes inside a zone to travel toward a second zone,
        to the time it takes inside a zone to return from a second, is equal to the ratio
        between the travel time from the first zone to the second, and the travel time from the
        second to the first.
    \item[5. Ambulance Placement] \hfill \\
        Ambulances can only be placed in the very center of a zone. Because we do not know the
        spacial position of the zones relative to each other, we cannot consider the ambulances
        being closer to one zone or another.
    \item[6. Partial Coverage] \hfill \\
        Partial ambulance coverage of a zone will be treated as incomplete even coverage over the entire
        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
        that multiple ambulances will cover different areas of the zones, thus evening out coverage. (If partial coverages from multiple ambulances sum to above the total population of a zone,
        we assume that zone is completely covered by the ambulances.)
\end{description}

@@

\subsection{Zone-to-Zone Population Dynamics}
An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as zone-to-zone coverage.
\begin{description}
    \item[$\mathbf{A(t), B(t)}$] \hfill \\
    	Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
    \item[$\mathbf{Z_{AB}(t)}$] \hfill \\
    	Zone-to-zone coverage of B from A
    \item[$\mathbf{v}$] \hfill \\
    	Required ambulance response time
    \item[$\mathbf{T_{AB}}$] \hfill \\
    	Travel time from A to B, given
    \item[$\mathbf{T_{BA}}$] \hfill \\
    	Travel time from B to A, given
    \item[$\mathbf{P_B}$] \hfill \\
    	Total population of B
    \item[$\mathbf{F_B(s)}$] \hfill \\
    	The probability curve for differences in travel time within B
   \item[$\mathbf{T_A}$] \hfill \\
    	Average travel time inside of A
    \item[$\mathbf{T_{A+}}$] \hfill \\
    	Average travel time in the direction of B to A inside of A
    \item[$\mathbf{T_{A-}}$] \hfill \\
    	Average travel time in the direction of A to B inside of A
   \item[$\mathbf{T_B}$] \hfill \\
    	Average travel time inside of B
    \item[$\mathbf{T_{B+}}$] \hfill \\
    	Average travel time in the direction of A to B inside of B
    \item[$\mathbf{T_{B-}}$] \hfill \\
    	Average travel time in the direction of B to A inside of B
    \item[$\mathbf{a, b}$] \hfill \\
    	Width of A and B respectively
    \item[$\mathbf{g}$] \hfill \\
    	Width of the gap between A and B
\end{description}

@@

\subsection{Ambulance Distribution Optimization}
Once the zone-to-zone coverages have been calculated, we must still decide where to place
the ambulances to maximize total coverage. Total coverage is defined as the sum of the coverages
of the individual zones, i.e. the number of people that can be reached by at least one ambulance
within eight minutes.

@@

\subsection{Localized Single Zone Disaster}
In a localized catastrophic event such as those that happened on September 11, 2001, there will be
many casualties in a single location that require aid. Ambulances, and other emergency vehicles,
such as police cars and fire trucks, will need to respond quickly in order to aid the most critically
injured first, who will be sorted by triage. Therefore, it is very important for ambulances to be able to
reach the emergency as quickly as possible, regardless of the initial location of the ambulances and the
location of the emergency.

@@

\bibliographystyle{chicago}
\bibliography{bibliography}
\end{document}

>>>>

\tableofcontents
\newpage
\section{Problem Restatement}
Given a fictitious district made up of six separate zones, and average travel times between zones, create a model to optimize the placement of $n$ ambulances in order to maximize the number of civilians reached in an eight minute period. Consider the scenarios where $n = 3$, $n = 2$, and $n = 1$, respectively, and for each scenario, keep track of how many people are not being reached with each possible solution.

Then, consider a scenario in which a large scale disaster affects a single location (i.e. 9/11), and discuss how an Emergency Service Coordinator would cover the situation. Examine how a real-world city or county would prepare for such a disaster. Finally, write a two page memo detailing the model and its analysis for the Emergency Service Coordinator.

\section{Assumptions and Justifications}
\begin{description}
    \item[1. Zone to Zone Travel] \hfill \\
    	The travel times given are calculated from an optimal route from the center of the first
        zone to the center of the second. This excludes the possibility of reaching a zone faster
        via an indirect route from the direct, given one.
    \item[2. Zone Interior Travel] \hfill \\
    	The travel times given for travel from any zone to itself is the average
        of all the travel times of the different routes within that zone.
    \item[3. Zone Directional Travel] \hfill \\
    	The ratio between the time it takes inside a zone to travel toward a second zone,
        to the time it takes inside a zone to return from a second, is equal to the ratio
        between the travel time from the first zone to the second, and the travel time from the
        second to the first.
    \item[4. Ambulance Placement] \hfill \\
        Ambulances can only be placed in the very center of a zone. Because we do not know the
        spacial position of the zones relative to each other, we cannot consider the ambulances
        being closer to one zone or another.
    \item[5. Partial Coverage] \hfill \\
        Partial ambulance coverage of a zone will be treated as incomplete even coverage over the entire
        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
        that multiple ambulances will cover different areas of the zones, thus evening out coverage. (If partial coverages from multiple ambulances sum to above the total population of a zone,
        we assume that zone is completely covered by the ambulances.)
\end{description}

@@

\subsection{Zone-to-Zone Population Dynamics}
An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as zone-to-zone coverage.
\begin{description}

    \item[$\mathbf{A(t), B(t)}$] \hfill \\
    	Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
    \item[$\mathbf{Z_{AB}(t)}$] \hfill \\
    	Zone-to-zone coverage of B from A
    \item[$\mathbf{v}$] \hfill \\
    	Required ambulance response time
    \item[$\mathbf{T_{AB}}$] \hfill \\
    	Travel time from A to B, given
    \item[$\mathbf{T_{BA}}$] \hfill \\
    	Travel time from B to A, given
    \item[$\mathbf{P_B}$] \hfill \\
    	Total population of B
    \item[$\mathbf{F_B(s)}$] \hfill \\
    	The probability curve for differences in travel time within B
   \item[$\mathbf{T_A}$] \hfill \\
    	Average travel time inside of A
    \item[$\mathbf{T_{A+}}$] \hfill \\
    	Average travel time in the direction of B to A inside of A
    \item[$\mathbf{T_{A-}}$] \hfill \\
    	Average travel time in the direction of A to B inside of A
   \item[$\mathbf{T_B}$] \hfill \\
    	Average travel time inside of B
    \item[$\mathbf{T_{B+}}$] \hfill \\
    	Average travel time in the direction of A to B inside of B
    \item[$\mathbf{T_{B-}}$] \hfill \\
    	Average travel time in the direction of B to A inside of B
    \item[$\mathbf{a, b}$] \hfill \\
    	Width of A and B respectively
    \item[$\mathbf{g}$] \hfill \\
    	Width of the gap between A and B
\end{description}

@@

\subsection{Ambulance Distributon Optimization}
Once the zone-to-zone coverages have been calculated, we must still decide where to place
the ambulances to maximize total coverage. Total coverage is defined as the sum of the coverages
of the individual zones, i.e. the number of people that can be reached by at least one ambulance
within eight minutes.

@@

\subsection{Localized Single Zone Disaster}
In a localized catastrophic event such as those that happened on September 11, 2001, there will be
many casualties in a single location that require aid. Ambulances, and other emergency vehicles,
such as police cars and fire trucks, will need to respond quickly in order to aid the most critically
injured first, who will be sorted by triage \cite{ColRev}. Therefore, it is very important for ambulances to be able to
reach the emergency as quickly as possible, regardless of the initial location of the ambulances and the
location of the emergency.

@@

\bibliographystyle{unsrt}
\bibliography{references}
\end{document}
